Epistemic Semantics in Guarded String Models

### 2020-06-18 tex/draft.tex
add separate language section

Formulas like the ones in \ex{event1} that describe pre- and
post-conditions are {\em effect formulas}. They are interpreted as
defining relations between valuations, as defined in Figure
\ref{effectfigure}.  The valuations they relate are constrained by the
state formula as well.  For the heads-tails example, let the state
formula and the effect formula for $a_1$ (Aly peeking at heads) be as
specified in \ex{effect}. Then the set of valuations determined by
$\rho$ and the relation on valuations for the event $u$ are \sem{rho}
and $\sem{\zeta}^{\sem{rho}}$ as given at the bottom in \ex{6}.  Given
a state formula $\rho$, the the relation characterizing pre- and
post-conditions of an event with effect formula $\zeta$ is defined to
be $\sem{\zeta}^{\sem{\rho}}$.

@@

\(
\begin{array}{cll}
  \sem{\rho} & = & \mbox{Set of Boolean valuations of} \\
            && \mbox{the atomic tests that verify $\rho$.} \\
\sem{\rho\,{:}\,\sigma}^V & = & (\sem{\rho}\cap V)\times(\sem{\sigma}\cap V)\\
\sem{\zeta{+}\eta}^V & = & \sem{\zeta}^V\cup\sem{\eta}^V\\
\sem{\zeta{\&}\eta}^V & = & \sem{\zeta}^V\cap\sem{\eta}^V\\
\sem{\bar{\zeta}}^V & = & V \times V \setminus \sem{\zeta}^V\\
\end{array}  
\)

@@

Kleene Algebra with Tests is an algebraic theory that is defined by
equations and inequalities, which a has model classes including
guarded string models, relational models, finite models, and matrix
models.  This paper focuses on defining a family of concrete guarded
string algebras, the elements of which are sets of guarded strings.
Definitions and notation mostly follow \cite{kozen2001automata}.
Additional syntax and semantics is included to model multi-agent
epistemic semantics.  Guarded strings over a finite alphabet {\sf{P}} are
like ordinary strings, but with truth assignments to a set $T$ of
primitive propositions (primitive tests) alternating with the symbols
from $E$. Following \cite{kozen2001automata}, we call these truth
assignments \emph{atoms}; the set of atoms is notated $\mathcal A$.
In the algebra described by Figure \ref{epikfigure}, $E$ is the set of
events $\{a_1,a_0,b_1,b_0\}$, and in the elevator example, $\{u,d\}$.
In the elevator example, $T$ is $\{p,q\}$, and in the coin example it
is $\{h,t\}$.  We write atoms as the boolean formulae that uniquely
specify the truth assignment. In the elevator example, we have atoms
$\bar q \bar p$, $\bar q p$, $q \bar p$, $q p$, for notational
simplicity we will write these as $\hat0$, $\hat1$, $\hat2$, $\hat3$
respectivelyto indicate the floor each atom represents. In the coin
example, we get $h\bar t$ and $\bar h t$ (for which we use the
shorthand $H$ and $T$), as well as the bogus atoms $\bar h \bar t$ and
$ht$!  To preclude bogosity, the \texttt{constraint} declaration in
Figure~\ref{epikfigure} describes the set of \emph{feasible atoms},
which we parse into a formula $\varphi$ (if there are multiple
\texttt{constraint} declarations, $\varphi$ is the conjunction of the
parsed formulae in each). For a formula $\phi$, the set of feasible atoms is
$\mathcal A_\phi$. In the coin example, the constraint $\varphi$ is
$h\bar t + \bar h t$. Since $\bar h t \models \varphi$ and $h \bar t
\models \varphi$, they are permitted feasible atoms, and since $\bar h
\bar t$ and $h t$ do not satisfy $\phi$ they are not permitted.

@@

\begin{example} \label{fusion1}
\hspace{-2mm}\(\hat 0 ~u~ \hat 1 ~u~ \hat 2 ~d~ \hat 1 \cdot \hat 1 ~u~ \hat 2 = \hat 0 ~u~ \hat 1 ~u~ \hat 2 ~d~ \hat 1 ~u~ \hat 2 \)

\hspace{-2mm}\( \hat 0 ~u~ \hat 1 ~u~ \hat 2 ~d~ \hat 1 \cdot \hat 2 ~u~ \hat 3 = \mbox{\em{undefined}} \)

\hspace{-2mm}\(H \cdot H ~a_0~ H = H ~a_0~ H \)

\hspace{-2mm}\(T \cdot T ~a_1~ T = \mbox{\em{undefined}} \)
\end{example}

@@

Fortunately, Epik provides a syntax to specify the input-output
behavior via the \texttt{event} declarations. From these we construct
a function $P$ from agents to relations on atoms that specify the
effects each action can have. If there are multiple event declarations
for the same event, only the latter one is incorporated. To construct
the effect relation $P(e)$ for event $e$, we add a pair $\alpha,
\beta$ to the relation $P(e)$ for every disjunct $\phi:\phi'$ such
that $\alpha \models \phi$ and $\beta \models \phi'$.  These have the
status of event types, in that they can ``happen'' in different
possible worlds. Here happening corresponds to incrementing the world
with some compatible element of the event type.  Where $e$ is a bare
event symbol, $\llbracket e \rrbracket^{\varphi,P}$ is the
corresponding set of guarded strings, consisting of the bare event
decorated with compatible truth assignments denoted by $P$ that are
admitted by the world-constraints $\varphi$.  See this formally in
Figure~\ref{fig:interp}, and the examples in \ex{events1}.
% u (\bar{q}\bar{p}):(\bar{q}p) + (\bar{q}p):(q\bar{p}) + (q\bar{p}):(qp) 173
% d (\bar{q}p):(\bar{q}\bar{p}) + (q\bar{p}):(\bar{q}p) + (qp):(q\bar{p})

@@

These operators combine to form the algebraic structure Kleene Algebra
with Tests (\textsc{Kat}), which has the algebraic signature
$\tuple{K,+,\cdot,*,\bar{},0,1}$.  We interpret each term in as a set
of guarded strings as indicated in Figure~\ref{fig:interp}. A bare
event $e$ is interpreted as the set of guarded strings allowed by
$\varphi$ and $P$. The operation $p + q$ is set union. The constant
$0$ is the empty set.  The constant 1 is the set of all truth
assignments obeying the constraint on truth assignments,
i.e. $\{10,01\}$ in the coin example.  The operation $\cdot$ is fusion
product raised to sets: $x \cdot y$ is the set of all defined fusion
products of an element of $x$ with and element of $y$.  The operation
$*$ is Kleene star, with $x* = \cup_{i\geq 0}x^i$, where $x^i$ is the
$i$-times product of $x$ with itself and $x^0=1$.  Subsets of $1$
indicated by $t$ are also elements of $K$, and these form the Boolean
algebra of tests, denoting all atoms admitted by the constraint
$\varphi$ and the boolean test $t$.  We ``overload'' $\cdot$ to
further indicate boolean conjunction, $+$ to further indicate boolean
disjunction, and $0,1$ to indicate the zero and one elements of the
boolean algebra. The overbar operation denotes complement in this
Boolean algebra: $\overline t$ denotes all atoms $\alpha$ such that
$\alpha \Rightarrow \neg t$.  Other boolean operators (such as
implication $\Rightarrow$) are encoded as syntactic sugar in the
standard way.

To this we add an unary operation $\Diamond_a$ for each agent $a$, and a
unary complent operation $\cdot^{c}$ on terms.  This results in the
signature $\tuple{K,+,\cdot,*,\bar{},0,1,{}^c,\Diamond_a,\Diamond_b}$
for epistemic KAT with two agents.  We interpret the epistemic
epistemic modality $\Diamond_a$ using Kripke semantics, as pre-image
relative to a fixed relation $R_a$ between guarded strings,
$\Diamond_a~x = \{u \mid \exists v. v \in x \wedge u \mathrel{R_a} v\}$.
Here $u$ and $v$ are guarded strings, while $x$ is an element of $K$.

@@

It remains to define the Kripke relation on guarded strings from an
agent specification as in Figure \ref{epikfigure}. In Epik, an agent
specification pairs each bare event with a set of ($+$-separated) bare
events, and so determines a relation between bare events, call it
relation $R_a$ for an agent $a$.  We can lift this to a relation
$\hat{R_a}$ between decorated events for a given $\varphi$ and $P$,
see \ex{Rhat}, and again to generalized to a relation $\doublehat{R}$
on arbitrary guarded strings by relational Kleene star (as opposed to
the Kleene star from aboce) , as defined in \ex{Rhathat}. The
operation $\cdot$ in the definition is KAT product, which enforces
matching of tests.

@@

\begin{example}   \label{Rhathat}
\hspace{-2mm}\(
\doublehat{R} \triangleq
\hspace{-2mm}\begin{array}[t]{l}
\{ \tuple{x,y} \mid \exists u_1 ... \exists u_n \exists v_1 ... \exists v_n. \\
\hspace{6mm} u_1\mathrel{R}v_1 \wedge ... \wedge u_n\mathrel{R}v_n \wedge\\
\hspace{6mm} x \in \llbracket u_1 \cdot ... \cdot u_n \rrbracket^{\varphi,P}\hspace{1mm} \wedge \\
\hspace{6mm} y \in \llbracket v_1 \cdot ... \cdot v_n \rrbracket^{\varphi,P} \hspace{2mm} \}
\end{array}
\)
\end{example}

@@

\begin{figure}
  \[\begin{array}{l >{\triangleq}c l}
  \llbracket 0 \rrbracket^{\varphi,P} && \{\} \\  
  \llbracket 1 \rrbracket^{\varphi,P} && \{\alpha \mid \alpha \Rightarrow \varphi\}\\
  \llbracket e \rrbracket^{\varphi,P}&& \{\alpha \cdot e \cdot \beta \mid
  (\alpha,\beta) \in P(e), \alpha, \beta \Rightarrow \varphi \}
  \\ \llbracket \_ \rrbracket^{\varphi,P}&& \bigcup_{e \in
    \dom(P)}\llbracket e \rrbracket^{\varphi,P}\\
  \llbracket t \rrbracket^{\varphi,P} &&  \{\alpha \mid \alpha \Rightarrow \varphi \wedge t\}\\
  \llbracket{p+q}\rrbracket^{\varphi,P} && \llbracket{p}\rrbracket^{\varphi,P} \cup \llbracket q \rrbracket^{\varphi,P}\\
  \llbracket{p \& q}\rrbracket^{\varphi,P} && \llbracket{p}\rrbracket^{\varphi,P} \cap \llbracket q \rrbracket^{\varphi,P}\\
  \llbracket{p;q}\rrbracket^{\varphi,P} && \llbracket p \rrbracket^{\varphi,P} \cdot \llbracket{q}\rrbracket^{\varphi,P}\\
  \llbracket p^*\rrbracket^{\varphi,P} && \displaystyle\bigcup_n {\underbrace{\llbracket p \rrbracket^{\varphi,P}\cdot \ldots \cdot \llbracket p \rrbracket^{\varphi,P}}_{n}} \\
  \llbracket \sim p \rrbracket^{\varphi,P} && \llbracket \_^*\rrbracket^{\varphi,P} \setminus \llbracket p \rrbracket^{\varphi,P} \\
  \llbracket \langle a \rangle~p \rrbracket && \doublehat{R_a}\llbracket p \rrbracket

@@

Summing up, given an Epik program with $n$ agents, we construct a
concrete guarded string model
$\tuple{K,+,\cdot,*,\bar{},0,1,{}^c,\Diamond_{a_1},...,\Diamond_{a_n}}$.
The elements of $K$ are interpreted as propositions.  $0^c$ is the set
of worlds, and it may be countably infinite.  $\Diamond_{a_i}$ is an
epistemic modality for the $i$th agent.  Or referring to the Kripke
relations $\doublehat{R}_i$, the construction defines a multi-agent
Kripke frame $\tuple{0^c,\doublehat{R}_1,...,\doublehat{R}_n}$
(usually a countable one) from an Epik specification. The frame
consists of a set of worlds, and an epistemic-alternative relation for
each agent.  These models are used as a target for natural-language
interpretation in Section 5 and Section 6, where we obtain semantic
values such as \sem{Amy knows that it's heads and Bob knows that Amy
  knows whether it is heads or tails, and does not know that it's
  heads} as elements of $K$. Concretely the proposositions are sets of
guarded strings (usually countable ones), construed as sets of worlds
as they figure in possible worlds semantics for natural language.

@@

\begin{figure}
\begin{tabular}{lll}
agents & $a,b...$ & $a {:}{:}{=} \, \tuple{\mbox{atomic agents}}$
\end{tabular}

\begin{tabular}{lll}
tests & $T,S...$ & $T{:}{:}{=} \, \begin{array}[t]{l}\tuple{\mbox{atomic tests}}\,|\,0\,|\,1\,|\\ T{+}S\;|\;T\,{;}\,S\;|\;!T\end{array}$
\end{tabular}

\begin{tabular}{lll}
propositions & $p,q...$ & \(p{:}{:}{=} \,
\begin{array}[t]{l}\tuple{\mbox{atomic events}}\,|\,\_\, |\\
T \,|\, 
p{+}q \,|\,
p\mbox{\&}q \,|\, \\
p{;}q \;|\;
p{*} \;|\; {\sim}p \;|\\
{\langle a \rangle}~p
\end{array}\)
\end{tabular}

\caption{The language of Epik terms. Propositional terms are interpreted
  as sets of guarded strings.}
\label{fig:epik-grammar}
\label{termfigure}
\end{figure}

>>>>

Formulas like the ones in \ex{event1} that describe pre- and
post-conditions are {\em effect formulas}. They are interpreted as
defining relations between valuations, as defined in Figure
\ref{effectfigure}.  The valuations they relate are constrained by the
state formula as well.  For the heads-tails example, let the state
formula and the effect formula for $a_1$ (Aly peeking at heads) be as
specified in \ex{effect}. Then the set of valuations determined by
$\rho$ and the relation on valuations for the event $u$ are
$\sem{\rho}$ and $\sem{\zeta}^{\sem{\rho}}$ as given at the bottom in
\ex{6}.  Given a state formula $\rho$, the the relation characterizing
pre- and post-conditions of an event with effect formula $\zeta$ is
defined to be $\sem{\zeta}^{\sem{\rho}}$.

@@

\(
\begin{array}{cll}
  \sem{\rho} & = & \mbox{Set of Boolean valuations of} \\
            && \mbox{the atomic tests that satisfy $\rho$.} \\
\sem{\rho\,{:}\,\sigma}^V & = & (\sem{\rho}\cap V)\times(\sem{\sigma}\cap V)\\
\sem{\zeta{+}\eta}^V & = & \sem{\zeta}^V\cup\sem{\eta}^V\\
\sem{\zeta{\&}\eta}^V & = & \sem{\zeta}^V\cap\sem{\eta}^V\\
\sem{\bar{\zeta}}^V & = & V \times V \setminus \sem{\zeta}^V\\
\end{array}  
\)

@@

Kleene Algebra with Tests is an algebraic theory that is defined by
equations and inequalities, which a has model classes including
guarded string models, relational models, finite models, and matrix
models.  This paper focuses on defining a family of concrete guarded
string algebras, the elements of which are sets of guarded strings.
Definitions and notation mostly follow \cite{kozen2001automata}.
Additional syntax and semantics is included to model multi-agent
epistemic semantics.  Guarded strings over a finite alphabet {\sf{P}}
are like ordinary strings, but with truth assignments to a set $T$ of
primitive propositions (primitive tests) alternating with the symbols
from $E$. Following \cite{kozen2001automata}, we call these truth
assignments \emph{atoms}; the set of atoms is notated $\mathcal A$.
In the algebra described by Figure \ref{epikfigure}, $E$ is the set of
events $\{a_1,a_0,b_1,b_0\}$, and in the elevator example, $\{u,d\}$.
In the elevator example, $T$ is $\{p,q\}$, and in the coin example it
is $\{h,t\}$.  We write atoms as the boolean formulae that uniquely
specify the truth assignment. In the elevator example, we have atoms
$\bar q \bar p$, $\bar q p$, $q \bar p$, $q p$, for notational
simplicity we will write these as $\hat0$, $\hat1$, $\hat2$, $\hat3$
respectivelyto indicate the floor each atom represents. In the coin
example, we get $h\bar t$ and $\bar h t$ (for which we use the
shorthand $H$ and $T$), as well as the bogus atoms $\bar h \bar t$ and
$ht$!  To preclude bogosity, the \texttt{constraint} declaration in
Figure~\ref{epikfigure} describes the set of \emph{feasible atoms},
which we parse into a formula $\varphi$ (if there are multiple
\texttt{constraint} declarations, $\varphi$ is the conjunction of the
parsed formulae in each). For a formula $\varphi$, the set of atoms
that satisfy $\varphi$ is $\mathcal A_\varphi$ -- these are the
feasible atoms. In the coin example, the constraint $\varphi$ is
$h\bar t + \bar h t$. Since $\bar h t$ satisfies $\varphi$ and $h \bar
t$ satisfies $\varphi$, they are permitted feasible atoms, and since
$\bar h \bar t$ and $h t$ do not satisfy $\varphi$ they are not
permitted. We omit boolean satisfiability since its definition is
standard.

@@

\begin{example} \label{fusion1}
\hspace{-2mm}\(\hat 0 ~u~ \hat 1 ~u~ \hat 2 ~d~ \hat 1 \diamond \hat 1 ~u~ \hat 2 = \hat 0 ~u~ \hat 1 ~u~ \hat 2 ~d~ \hat 1 ~u~ \hat 2 \)

\hspace{-2mm}\( \hat 0 ~u~ \hat 1 ~u~ \hat 2 ~d~ \hat 1 \diamond \hat 2 ~u~ \hat 3 = \mbox{\em{undefined}} \)

\hspace{-2mm}\(H \diamond H ~a_0~ H = H ~a_0~ H \)

\hspace{-2mm}\(T \diamond T ~a_1~ T = \mbox{\em{undefined}} \)
\end{example}

@@

Fortunately, Epik provides a syntax to specify the input-output
behavior via the \texttt{event} declarations. From these we construct
a function $P$ from agents to relations on atoms that specify the
effects each action can have. If there are multiple event declarations
for the same event, only the latter one is incorporated. To construct
the effect relation $P(e)$ for event $e$, we add a pair $\alpha,
\beta$ to the relation $P(e)$ for every disjunct $\varphi:\varphi'$ such
that $\alpha$ satisfies $\phi$ and $\beta$ satisfies $\varphi'$.  These have the
status of event types, in that they can ``happen'' in different
possible worlds. Here happening corresponds to incrementing the world
with some compatible element of the event type.  Where $e$ is a bare
event symbol, $\llbracket e \rrbracket^{\varphi,P}$ is the
corresponding set of guarded strings, consisting of the bare event
decorated with compatible truth assignments denoted by $P$ that are
admitted by the world-constraints $\varphi$.  See this formally in
Figure~\ref{fig:interp}, and the examples in \ex{events1}.
% u (\bar{q}\bar{p}):(\bar{q}p) + (\bar{q}p):(q\bar{p}) + (q\bar{p}):(qp) 173
% d (\bar{q}p):(\bar{q}\bar{p}) + (q\bar{p}):(\bar{q}p) + (qp):(q\bar{p})

@@

\section{A Language for Epistemic Sets of Guarded Strings}

To reason about epistemic alternatives, guarded strings are used to
represent different possible worlds, so agents' knowledge/beliefs are
represented by sets of guarded strings. The standard algebra for
manipulating guarded strings is Kleene Algebra with Tests
(\textsc{KAT}), which has the algebraic signature
$\tuple{K,+,;,*,\bar{},0,1}$ \cite{kozen2001automata}. However, the
KATs don't permit native reasoning about modal operators, so Epik's
signature needs to subsume the KAT operators.

Figure~\ref{fig:epik-grammar} depicts the syntax of Epik's formal
term language. As in KAT, $0$ is the null element, $1$ is the unit
element, $+$ indicates disjuction, $;$ indicates event sequencing or
boolean conjunction, $!$ indicates boolean negation, and $*$ indicates
iteration. We add some additional operations to reason about epistemic
alternatives: the term $\Diamond_a~p$ represents epistemic possibility
for agent $a$ in worlds $p$, and complement $\neg p$ represents the
worlds not described by $p$. We can encode $\Box_a~p$, i.e. epistemic
certainty for agent $a$ in worlds $p$, by $\Box_a~p =
(\Diamond_a~p^c)^c$.

\begin{figure}

  \[\begin{array}{l>{\hspace{-.5em}}c>{\hspace{-0.75em}}l}
  \multicolumn 2 l {\textrm{tests}}& a~\textrm{is an atomic test} \\
  t,s & ::=& a~|~0~|~1~|~t+t~|~t;t~|~!t\\
  \multicolumn 2 l {\textrm{terms}} & e~\textrm{is an atomic event} \\
  p,q & ::=& e~|~0~|~1~|~t~|~p+p~|~p;p~|~p^*~|\neg p~|\Diamond_a~p
  \end{array}\]

  Derived Operators\\
  \mbox{}\qquad \(\Box_a p \triangleq \neg\Diamond_a\neg p \qquad p\&q \triangleq \neg(\neg p + \neg q) \)

\caption{The language of Epik terms and key derived
  operators}
\label{fig:epik-grammar}
\label{termfigure}
\end{figure}

We interpret each term in as a set of guarded strings as indicated in
Figure~\ref{fig:interp}. The function $\llbracket p
\rrbracket^{\varphi,P}$ interprets a term $p$ as a set of guarded
strings consistent with state constraints $\varphi$ and effect
relation $P$. A bare event $e$ is interpreted as the set of guarded
strings allowed by $\varphi$ and $P$. The constant $0$ is interpreted
as the empty set.  The constant $1$ is interpreted as the set of all
atoms obeying $\varphi$, i.e. $\{h\bar t, \bar h t\}$ in the coin
example. The operation $p + q$ is interpreted as the union of the
interpretations of $p$ and $q$. The operation $p;q$ interpreted as the
fusion product of the interpretations of $p$ and $q$ raised to sets:
$X \diamond Y = \{ x \diamond y \mid x \in X, y \in Y, x\diamond
y~\textit{defined}\}$.  The operation $p*$ is Kleene star, which is
interpreted to be least upper bound of the iterated fusion product of
the denotation of $p$ with itself. Subsets of $1$ indicated by $t$ are
also elements of $K$, and these form the Boolean algebra of tests,
denoting all atoms admitted by the constraint $\varphi$ and the
boolean test $t$.  We ``overload'' $;$ to further indicate boolean
conjunction, $+$ to further indicate boolean disjunction, and $0,1$ to
indicate the zero and one elements of the boolean algebra. The overbar
operation denotes complement in this Boolean algebra: $\overline t$
denotes all atoms $\alpha$ such that $\alpha \Rightarrow \neg t$.
Other boolean operators (such as implication $\Rightarrow$) are
encoded as syntactic sugar in the standard way. A boolean test $t$
denotes the set of atoms that satisfy $t;\varphi$, that is, they
satisfy both $t$ and $\varphi$.

The unary epistemic alternative operation $\Diamond_a$ for each agent
$a$, is interpreted using using Kripke semantics, as pre-image
relative to a fixed relation $\hat{R_a}$ between guarded strings,
$\Diamond_a~x = \{u \mid \exists v. v \in x \wedge u \mathrel{R_a}
v\}$.  Here $u$ and $v$ are guarded strings, while $x$ is an element
of $K$.

@@

It remains to define the Kripke relation on guarded strings from an
agent specification as in Figure \ref{epikfigure}. In Epik, an agent
specification pairs each bare event with a set of ($+$-separated) bare
events, and so determines a relation between bare events, call it
relation $R_a$ for an agent $a$.  We can lift this to a relation
$\hat{R_a}$ between guarded strings, as defined in \ex{Rhathat}. The
operation $(\mathop;)$ in the definition is KAT product, which enforces
matching of tests.

@@

\begin{example}   \label{Rhathat}
\hspace{-2mm}\(
\hat{R} \triangleq
\hspace{-2mm}\begin{array}[t]{l}
\{ \tuple{x,y} \mid \exists u_1 ... \exists u_n \exists v_1 ... \exists v_n. \\
\hspace{6mm} u_1\mathrel{R}v_1 \wedge ... \wedge u_n\mathrel{R}v_n \wedge\\
\hspace{6mm} x \in \llbracket u_1 ; ... ; u_n \rrbracket^{\varphi,P}\hspace{1mm} \wedge \\
\hspace{6mm} y \in \llbracket v_1 ; ... ; v_n \rrbracket^{\varphi,P} \hspace{2mm} \}
\end{array}
\)
\end{example}

@@

\begin{figure}
  \[\begin{array}{l >{\triangleq}c l}
  \llbracket 0 \rrbracket^{\varphi,P} && \{\} \\  
  \llbracket 1 \rrbracket^{\varphi,P} && \{\alpha \mid \alpha \in \mathcal A_\varphi\}\\
  \llbracket e \rrbracket^{\varphi,P}&& \{\alpha~e~\beta \mid
  (\alpha,\beta) \in P(e), \alpha, \beta \Rightarrow \varphi \}
  \\ \llbracket \_ \rrbracket^{\varphi,P}&& \bigcup_{e \in
    \dom(P)}\llbracket e \rrbracket^{\varphi,P}\\
  \llbracket t \rrbracket^{\varphi,P} &&  \{\alpha \mid \alpha \in \mathcal A_{\varphi;t}\}\\
  \llbracket{p+q}\rrbracket^{\varphi,P} && \llbracket{p}\rrbracket^{\varphi,P} \cup \llbracket q \rrbracket^{\varphi,P}\\
  \llbracket{p;q}\rrbracket^{\varphi,P} && \llbracket p \rrbracket^{\varphi,P} \diamond \llbracket{q}\rrbracket^{\varphi,P}\\
  \llbracket p^*\rrbracket^{\varphi,P} && \displaystyle\bigcup_n {\underbrace{\llbracket p \rrbracket^{\varphi,P}\diamond \ldots \diamond \llbracket p \rrbracket^{\varphi,P}}_{n}} \\
  \llbracket \neg p \rrbracket^{\varphi,P} && \llbracket \_^*\rrbracket^{\varphi,P} \setminus \llbracket p \rrbracket^{\varphi,P} \\
  \llbracket \langle a \rangle~p \rrbracket && \{x \mid x~\hat{R_a}~y, y \in \llbracket p \rrbracket\}

@@

Summing up, given an Epik program with $n$ agents, we construct state
constraints $\varphi$, effect relations $P$, and a concrete guarded
string model for each term using $\llbracket -
\rrbracket^{\varphi,P}$.
%% $\tuple{K,+,;,*,\bar{},0,1,{}^c,\Diamond_{a_1},...,\Diamond_{a_n}}$.
 $0^c$ is the set of worlds, and it may be countably infinite.
$\Diamond_{a_i}$ is an epistemic modality for the $i$th agent.  Or
referring to the Kripke relations $\hat{R}_i$, the construction
defines a multi-agent Kripke frame
$\tuple{0^c,\hat{R}_1,...,\hat{R}_n}$ (usually a countable one) from
an Epik specification. The frame consists of a set of worlds, and an
epistemic-alternative relation for each agent.  These models are used
as a target for natural-language interpretation in Section 5 and
Section 6, where we obtain semantic values such as \sem{Amy knows that
  it's heads and Bob knows that Amy knows whether it is heads or
  tails, and does not know that it's heads} as elements of
$K$. Concretely the proposositions are sets of guarded strings
(usually countable ones), construed as sets of worlds as they figure
in possible worlds semantics for natural language.

@@
